Criteria for evaluating reproducibility

### 2017-04-04 reproducibility_criteria.Rmd
Add reproducibility tibble to reproducibility criteria Rmd

>>>>

# Example of reproducibility `tibble`

```{r}
reproducibility <- tibble::tibble(
  Article = "The Area Under the Disease Progress Stairs: Calculation, Advantage, and Application",
  DOI = "PHYTO-07-11-0216",
  Journal = "Phytopathology",
  Authors =  "Ivan Simko and Hans-Peter Piepho",
  Year = 2012,
  Vol = 102,
  Iss = 4,
  pp = "381-389",
  IF = 3.011,
  Journal_class = "Fundamental",
  Page_charges = 130,
  Country =  "USA",
  Open_or_Restricted = "Optional",
  Reproducibility_instructions = FALSE,
  Iss_per_Year = 12,
  Supl_mats = TRUE,
  Comp_methods_availability = 2,
  Software_availability = 1,
  Software_citation = 3,
  Analysis_automation = 0,
  Data_availability = 0,
  Data_annotation = 0,
  Data_tidiness = 0
)

reproducibility <- dplyr::mutate(reproducibility,
                                 Reproducibility_score = sum(Comp_methods_availability,
                                                             Software_availability,
                                                             Software_citation,
                                                             Analysis_automation,
                                                             Data_availability,
                                                             Data_annotation,
                                                             Data_tidiness))

reproducibility

reproducibility$Reproducibility_score
```
